Approximation as Differentiation: Notes

### 2025-05-19 notes/cmon-enriched.tex
Clean up CMon-enriched Yoneda preserves biproducts.

The $\CMon$-enriched Yoneda embedding preserves biproducts, where (as in any functor category) biproducts in
$\PSh_{\CMon}(\cat{C})$ are computed pointwise.

>>>>

\todo{Generalise to any monoidal closed $\mathscr{V}$ with biproducts?} $\CMon$ is monoidal closed, and has
biproducts (\secref{categories-with-biproducts:cmon}) which are inherited pointwise into
$\PSh_{\CMon}(\cat{C})$ and preserved by the $\CMon$-enriched Yoneda embedding.
